STR: Seasonal-Trend decomposition using Regression

### 2021-07-01 accepted/str_accepted.tex
Accepted version for arxiv

% Private macros here (check that there is no clash with the style)

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{str_ijds_files/figure-latex/examples-1.pdf}
\caption{\label{fig:examples}Examples of time series generated by the two DGPs.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{str_ijds_files/figure-latex/supermarket-1.pdf}
\caption{\label{fig:supermarket}Supermarket and grocery store log revenue in New South Wales, decomposed with STR. The original data (logged) are shown in the top panel, while the components are shown in the other panels, with 95\% confidence intervals for the trend and season components in blue}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{str_ijds_files/figure-latex/vic-1.pdf}
\caption{\label{fig:vic}Electricity demand in Victoria, decomposed using STR. The original data are plotted in black in the first panel, with the decomposed trend plotted in red. The subsequent panels contain the weekly seasonal pattern; the daily seasonal pattern with complex topology; the effect of temperature in Melbourne, which has a daily seasonal pattern with complex topology; the effect of squared temperatures in Melbourne, which is allowed to vary over time; and the residuals. Grey vertical lines represent the residuals with the largest absolute values.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{str_ijds_files/figure-latex/MelTemp-1.pdf}
\caption{\label{fig:MelTemp}The temperature in Melbourne on 1 February 2000, and the following ten days. Ten red lines (two groups of five lines each) mark the times of the outliers. The first group spans 14:30--17:00 on 3 February, while the second group spans 15:30--18:00 on the following day.}
\end{figure}

>>>>

\long\def\theARTICLETOPLEFT{{\tabcolsep0pt\fs.12.14.\bf
\begin{tabular}{l}\HD{25}{0}Accepted for publication at the {\bi\theJOURNAL}\\
manuscript {\theMANUSCRIPTNO}\end{tabular}}}%
\RRHSecondLine{\fs.7.9.\rm Article accepted for {\it\theJOURNAL}}% default
\LRHFirstLine{\bf\theRUNAUTHOR:\enskip {\it\theRUNTITLE}}% default
\LRHSecondLine{\fs.7.9.\rm Article accepted for {\it\theJOURNAL}}% default

\def\theARTICLETOP{%
  \vspace*{-57pt}
  \begin{Center}
  \parbox[t][60pt][t]{\textwidth}{%
  \theARTICLETOPLEFT\hfill\theARTICLETOPRIGHT}
  \vspace*{12pt}
  \end{Center}}

% Private macros here (check that there is no clash with the style)
\usepackage[no-weekday]{eukdate}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{examples-1.pdf}
\caption{\label{fig:examples}Examples of time series generated by the two DGPs.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{supermarket-1.pdf}
\caption{\label{fig:supermarket}Supermarket and grocery store log revenue in New South Wales, decomposed with STR. The original data (logged) are shown in the top panel, while the components are shown in the other panels, with 95\% confidence intervals for the trend and season components in blue}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{vic-1.pdf}
\caption{\label{fig:vic}Electricity demand in Victoria, decomposed using STR. The original data are plotted in black in the first panel, with the decomposed trend plotted in red. The subsequent panels contain the weekly seasonal pattern; the daily seasonal pattern with complex topology; the effect of temperature in Melbourne, which has a daily seasonal pattern with complex topology; the effect of squared temperatures in Melbourne, which is allowed to vary over time; and the residuals. Grey vertical lines represent the residuals with the largest absolute values.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{MelTemp-1.pdf}
\caption{\label{fig:MelTemp}The temperature in Melbourne on 1 February 2000, and the following ten days. Ten red lines (two groups of five lines each) mark the times of the outliers. The first group spans 14:30--17:00 on 3 February, while the second group spans 15:30--18:00 on the following day.}
\end{figure}
